---
name: Michael J.
surname: Root
position: "Assistant Professor of Psychology"
address: "Department of Psychology, Bridgewater State University, Bridgewater, MA 02325"
phone: +1 518 531 1958
email: "m1root@bridgew.edu"
github: michaeljroot
researchgate: Michael_Root3
orcid: 0000-0003-3857-6673
googlescholar: 0jAWWcYAAAAJ&hl
profilepic: MJR.jpg
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Education

```{r education}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Doctor of Philosophy, Psychology", "1999 --- 2005", "University of New Hampshire", "Durham, NH",
  "Certificate of Advanced Graduate Study, General Psychology", "1998 --- 1999", "Springfield College", "Springfield, MA",
  "Master of Science, Mental Health Counseling", "1996 --- 1998", "Springfield College", "Springfield, MA",
  "Bachelor of Science, Psychology", "1988 --- 1992", "Springfield College", "Springfield, MA",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Teaching Experience
```{r teaching experience}
tribble(
  ~ title, ~ what, ~ year, ~where, ~ detail, 
  "Bridgewater State University---Assistant Professor of Psychology", "Courses Taught", "2017 --- Present", "Bridgewater, MA", "Statistics for Psychology",
  "Bridgewater State University---Assistant Professor of Psychology", "Courses Taught", "2017 --- Present","Bridgewater, MA", "Research Methods in Psychology",
  "Bridgewater State University---Assistant Professor of Psychology", "Courses Taught", "2017 --- Present","Bridgewater, MA", "Conducting Research: Research Methods II",
  "Bridgewater State University---Assistant Professor of Psychology", "Courses Taught", "2017 --- Present","Bridgewater, MA", "Social Psychology",
  "Bridgewater State University---Assistant Professor of Psychology", "Courses Taught", "2017 --- Present","Bridgewater, MA", "Internship: Peer Assisted Learning",
  "Bridgewater State University---Assistant Professor of Psychology", "Courses Taught", "2017 --- Present","Bridgewater, MA", "Research",
  "Bridgewater State University---Full-Time, Temporary Assistant Professor of Psychology", "Courses Taught", "2016 --- 2017","Bridgewater, MA", "Statistics for Psychology",
  "Bridgewater State University---Full-Time, Temporary Assistant Professor of Psychology", "Courses Taught", "2016 --- 2017","Bridgewater, MA", "Research Methods in Psychology",
  "Bridgewater State University---Full-Time, Temporary Assistant Professor of Psychology", "Courses Taught", "2016 --- 2017","Bridgewater, MA", "Social Psychology",
  "Minnesota State University, Moorhead---Fixed-Term Assistant Professor of Psychology","Courses Taught", "2015 --- 2016", "Moorhead, MN", "General Psychology",
  "Minnesota State University, Moorhead---Fixed-Term Assistant Professor of Psychology", "Courses Taught","2015 --- 2016", "Moorhead, MN", "Experimental Psychology",
  "Minnesota State University, Moorhead---Fixed-Term Assistant Professor of Psychology", "Courses Taught","2015 --- 2016", "Moorhead, MN", "Social Psychology",
  "Minnesota State University, Moorhead---Fixed-Term Assistant Professor of Psychology", "Courses Taught","2015 --- 2016", "Moorhead, MN", "Learning and Memory",
  "Bridgewater State University---Full-Time, Temporary Assistant Professor of Psychology", "Courses Taught","2013 --- 2015","Bridgewater, MA", "Statistics for Psychology",
  "Bridgewater State University---Full-Time, Temporary Assistant Professor of Psychology", "Courses Taught","2013 --- 2015","Bridgewater, MA", "Social Psychology",
  "Bridgewater State University---Full-Time, Temporary Assistant Professor of Psychology", "Courses Taught","2013 --- 2015","Bridgewater, MA", "Psychology of Learning",
  "Bridgewater State University---Full-Time, Temporary Assistant Professor of Psychology", "Courses Taught","2013 --- 2015","Bridgewater, MA", "Research Methods in Psychology",
  "Bridgewater State University---Full-Time, Temporary Assistant Professor of Psychology", "Courses Taught","2013 --- 2015","Bridgewater, MA", "Introduction to Psychology",
  "Coastal Carolina University---Assistant Professor of Psychology","Courses Taught", "2006 --- 2009","Conway, SC", "General Psychology (including Honors)",
  "Coastal Carolina University---Assistant Professor of Psychology","Courses Taught", "2006 --- 2009","Conway, SC", "Introduction to Scientific Communication: Psychological Perspectives",
  "Coastal Carolina University---Assistant Professor of Psychology","Courses Taught", "2006 --- 2009","Conway, SC", "Research Methods",
  "Coastal Carolina University---Assistant Professor of Psychology","Courses Taught", "2006 --- 2009","Conway, SC", "Cognitive Processes (including Honors)",
  "Coastal Carolina University---Assistant Professor of Psychology","Courses Taught", "2006 --- 2009","Conway, SC", "History and Psychology of Psychology",
  "Ohio University---Visiting Assistant Professor of Psychology","Courses Taught", "2004 --- 2006","Athens, OH", "General Psychology",
  "Ohio University---Visiting Assistant Professor of Psychology","Courses Taught", "2004 --- 2006","Athens, OH", "Elementary Statistical Reasoning",
  "Ohio University---Visiting Assistant Professor of Psychology","Courses Taught", "2004 --- 2006","Athens, OH", "Statistics for the Behavioral Sciences",
  "Ohio University---Visiting Assistant Professor of Psychology","Courses Taught", "2004 --- 2006","Athens, OH", "Human Learning and Cognitive Processes",
  "Ohio University---Visiting Assistant Professor of Psychology","Courses Taught", "2004 --- 2006","Athens, OH", "History and Systems of Psychology (Graduate)",
)%>% 
  detailed_entries(
    with = title,
    what = what,
    why = detail,
    when = year,
    where = where
  )
```

# Research Interests

* Public Understanding of Psychology
  - Psychology Myth Prevalence
* Pedagogical Topics
  - Moral Evaluation of Educational Categories
  - Student Entitlement
* Cheater Detection in Social Exchange
  - Source Memory for Faces of Cheaters 
* Cognitive Biases in Risky Decisions
  * Border Bias Heuristic
  * Better-Than-Average Effect on Environmental Conservation
* 20th Century History of Psychology
  * Interdisciplinarity
  * Boundary-Work
* Modern and Robust Statistical Procedures

# Funding and Professional Development

```{r funding}
tribble(
  ~ award, ~ about, ~ year, ~ where, ~ amount,
  "ATP Summer Grant Mentorship", "Student Research Mentor", "2019", "Bridgewater State University", "$2000",
  "Professional Development Award", "Professional Development" , "2019", "Bridgewater State University", "$827",
  "Professional Development Award", "Professional Development", "2018", "Bridgewater State University", "$838",
  "CARS Research Grant", "Project: Content Analysis of Current History and Systems of Psychology Textbooks", "2017", "Bridgewater State University", "$2,000",
  "Office of Undergraduate Research", "APS Conference Registration", "2017", "Bridgewater State University", "$325",
  "Professional Development Award", "Professional Development", "2017", "Bridgewater State University", "$844",
  "Professional Development Award", "Professional Development", "2016", "Bridgewater State University", "$821",
  "Professional Development Award", "Professional Development", "2014", "Bridgewater State University", "$750",
  "SOTL Grant, Center for Effective Teaching and Learning", "Project: Using WebCT to Enhance Test Performance", "2006", "Coastal Carolina University", "$2,500",
  "Graduate Summer Research Grants", "Various Research Projects", "2001---2003", "University of New Hampshire", "$1,000/Summer",
)%>% 
  detailed_entries(
    with = award,
    what = about,
    why = amount,
    when = year,
    where = where
)
```

# Dissertation

Boundary-Work in United States Psychology: A Study of Three Interdisciplinary Programs  
(William R. Woodward, Chairperson)

# Publications

\hangindent=0.7 cm Root, M. J. & Stanley, C. M. (2018). Class dis-mythed: Exploring the prevalence and perseverance of myths in upper-level psychology courses. In R. L. Miller and A. Martinez (Eds.). \emph{Teaching Tips: A Compendium of Conference Presentations on Teaching, 2016-2017}. Retrieved from the Society for the Teaching of Psychology web site: http://teachpsych.org/ebooks/    

\hangindent=0.7 cm Root, M. J. (2015). Thriving in a stressful world. [Review of the book \emph{Hardiness: Turning stressful circumstances into resilient growth}, by S. R. Maddi]. \emph{Journal of Constructivist Psychology, 29}(3), 335-337. doi:10.1080/10720537.2015.1071212

\hangindent=0.7 cm Root, M. J. (2013). Social psychology. \emph{Office of Teaching Resources in Psychology}. http://teachpsych.org/Resources/Documents/otrp/syllabi/MR14social.pdf

\hangindent=0.7 cm Root, M. J. (2011). [Review of the book \emph{A conceptual history of psychology}, by J. D. Greenwood]. \emph{Journal of the History of the Behavioral Sciences, 47}, 116-117.

\hangindent=0.7 cm Root, M. J. (2009). The evolution of psychologists’ recommended child-rearing practices in the United States. In Zhukov, R., Mardahaev, L., DeCenzo, D., & Wiseman, D. (Eds.) \emph{Family and Childrearing: Russia and the USA, A Cross-Cultural Analysis}. Moscow, Russia: Russia State Social University Press.

\hangindent=0.7 cm Root, M. J. (2009). [Review of the book \emph{Borrowed knowledge: Chaos theory and the challenge of learning across disciplines}, by S. H. Kellert]. \emph{Journal of the History of the Behavioral Sciences, 45}, 395-396.

\hangindent=0.7 cm Root, M. J. (2008). The evolution of psychologists' recommended child-rearing practices in the United States. In Wiseman, D. G. (Ed.). \emph{The American Family: Understanding its Changing Dynamics and Place in Society} (pp. 97-111). Springfield, IL: Charles C. Thomas.

\hangindent=0.7 cm Root. M. J. (2008). The origins of psychiatric care in Germany. [Review of the book \emph{The University Department of Psychiatry in Munich: From Kraepelin and his predecessors to molecular psychiatry}, by H. Hippius, H. Möller, N. Müller, & G. Neundörfer-Kohl]. \emph{PsycCRITIQUES, 53}(24).

\hangindent=0.7 cm Root, M. J. (2006). The power of group processes: Unrecognized forces in historical change. [Review of the book \emph{Past impersonal: Group process in human history}, by R. Binion]. \emph{PsycCRITIQUES, 51}(9).

\hangindent=0.7 cm Root, M. J. (2006). Francis Galton. In G. L. Albrecht (Ed.), \emph{Encyclopedia of Disability} (Vol. 2, pp. 758-759). Thousand Oaks, CA: Sage.

\hangindent=0.7 cm Root, M. J. (2005). Keller, Fred S. In Carnes, M. C. (Ed.). \emph{American National Biography} (Supplement 2, pp. 305-307). New York, NY: Oxford University Press.

\hangindent=0.7 cm Root, M. J. (2003). [Review of the book \emph{Sir Francis Galton: From African exploration to the birth of eugenics}, N. W. Gillham]. \emph{Journal of the History of the Behavioral Sciences, 39}, 393-395.

\hangindent=0.7 cm Root, M. J. (2003). Great psychologists. \emph{Office of Teaching Resources in Psychology}. http://teachpsych.org/resources/Documents/otrp/syllabi/mr02historyf.pdf

\hangindent=0.7 cm Root, M. J. (2002). Introduction to psychology. \emph{Office of Teaching Resources in Psychology}. http://teachpsych.org/resources/Documents/otrp/syllabi/mr01introf.pdf

\hangindent=0.7 cm Root, M. J. (2002). [Review of the book \emph{Fighting for the good cause: Reflections on Francis Galton’s legacy to American hereditarian psychology}, by G. Sweeney]. \emph{The Cheiron Newsletter, Spring-Summer, 28}, 7.

\hangindent=0.7 cm Root, M. J. (1998, April). Conference Report: The Sixth Annual Winter Chaos Conference. \emph{Society for Chaos Theory in Psychology and the Life Sciences Newsletter, 5}, 1-2.

# Presentations 

## Peer-Reviewed Conference Presentations

(**bold** indicates student collaborators)

\hangindent=0.7 cm Root, M. J., Hayes-Bohanan, P., & Spievak, E. R. (2020, August --- November). \emph{Do librarians really wear halos? The moral value of libraries and their workers}. [Poster session]. 2020 New England Library Association Conference. http://nelib.org/news/upcoming-events/ (Poster sessions cancelled)

\hangindent=0.7 cm **Faria, C. M.**, Root, M. J., & Spievak, E. R. (2020, June 1 --- September 1). \emph{More human than humane: Stereotype content model perceptions on the mentally ill}. [Poster session]. 2020 Association for Psychological Science Conference, Chicago, IL. https://www.psychologicalscience.org/2020-virtual-poster

\hangindent=0.7 cm **Wasserman, N. B., Fitian, A. A.**, Root, M. J., & Spievak, E. R. (2020, June 1 --- September 1). \emph{Guiding metaphors: Entitlement, grade expectation, and educational values}. [Poster session]. 2020 Association for Psychological Science Conference, Chicago, IL. https://www.psychologicalscience.org/2020-virtual-poster

\hangindent=0.7 cm Root, M. J., Hayes-Bohanan, P., & Spievak, E. R. (2020, May). \emph{Librarians as boundary-objects: Creating a new role for information scientists in interdisciplinary research}. 2020 May CARS Celebration. Bridgewater, Ma. (Conference cancelled)

\hangindent=0.7 cm **Tang, M.**, & Root, M. J. (2020, April --- May). \emph{The moral evaluation of college-related items}. [Poster session]. 2020 StARS Virtual Conference, Bridgewater, MA.

\hangindent=0.7 cm **Durocher, B. R.**, Root, M. J., & Spievak, E. R. (2019, November). \emph{Myth trusters: Psychology myth prevalence in introductory psychology students}. [Poster session]. 2019 New England Psychological Association Conference, Manchester, NH.

\hangindent=0.7 cm **Tang, M.**, & Root, M. J. (2019, November). \emph{Judgment day: The moral evaluation of college-related items}. [Poster session]. 2019 New England Psychological Association Conference, Manchester, NH. 

\hangindent=0.7 cm **Bernique, A.**, & Root, M. J. (2019, June). \emph{Line in the sand: Is border bias evidence of an environmental threat response mechanism?} [Poster session]. 2019 Northeastern Evolutionary Psychology Society Conference, Boston, MA.

\hangindent=0.7 cm Root, M. J., **LePage, J.**, **Brenner, S.**, & **Gomm, A.** (2019, May). \emph{Double trouble: Psychology undergraduates’ misconceptions about twins}. [Poster session]. 2019 Association for Psychological Science Conference, Washington, DC.

\hangindent=0.7 cm Root, M. J., Ramos-Goyette, S., & **Logan, J. F.** (2019, May). Myth-told tales: \emph{Neuromyth prevalence in undergraduate biopsychology students}. [Poster session]. 2019 Association for Psychological Science Conference, Washington, DC.

\hangindent=0.7 cm **Fitian, A.**, Root, M. J., & Spievak, E. (2019, May). \emph{No A’s for effort: The relationship between entitlement and college students’ grade expectations}. [Poster session]. 2019 Association for Psychological Science Conference, Washington, DC.

\hangindent=0.7 cm Root, M. J., Ramos-Goyette, S., & **Logan, J. F.** (2019, April). \emph{Myth-told tales: Neuromyth prevalence in undergraduate biopsychology students}. [Poster session]. 2019 Student Arts and Research Symposium (StARS), Bridgewater State University, Bridgewater, MA.

\hangindent=0.7 cm **Fitian, A.**, Root, M. J., & Spievak, E. (2019, April). \emph{No A’s for effort: The relationship between entitlement and college students’ grade expectations}. [Poster session]. 2019 Student Arts and Research Symposium (StARS), Bridgewater State University, Bridgewater, MA.

\hangindent=0.7 cm Root, M. J. & **Bourget, I.** (2017, May). \emph{Myth-taken knowledge: Psychology myth prevalence in introductory psychology students}. [Poster session]. 2017 Association for Psychological Science Conference, Boston, MA.

\hangindent=0.7 cm **Bourget, I.**, **Carlson, T.**, **Pollack, K.**, & Root, M. J. (2017, May). \emph{Should I stay or should I go?: Questioning the evidence for border bias}. [Poster session]. 2017 Association for Psychological Science Conference, Boston, MA.

\hangindent=0.7 cm **Birkholz, S.**, Hessler, E., & Root, M. J. (2017, April). \emph{Retroactive interference effects on procedural memory}. [Poster session]. 2017 Midwestern Psychological Association Conference, Chicago, IL.

\hangindent=0.7 cm **Bourget, I**. & Root, M. J. (2017, April). \emph{Myth-taken knowledge: Psychology myth prevalence in introductory psychology students}. [Poster session]. 2017 Student Arts and Research Symposium, Bridgewater State University (StARS), Bridgewater, MA.

\hangindent=0.7 cm **Bourget, I.**, **Carlson, T.**, **Pollack, K.**, & Root, M. J. (2017, April). \emph{Should I stay or should I go?: Questioning the evidence for border bias}. [Poster session]. 2017 Student Arts and Research Symposium (StARS), Bridgewater State University, Bridgewater, MA.

\hangindent=0.7 cm Root, M. J. & Stanley, C. M. (2017, January). \emph{Class dis-mythed: Exploring the prevalence and perseverance of myths in upper-level psychology courses}. [Poster session]. 2017 National Institute on the Teaching of Psychology, St. Pete Beach, FL.

\hangindent=0.7 cm **Comeau, R. L.**, **Guaraldi, B. M.**, Root, M. J., **Molloy, B. K.**, & Spievak, E. R. (2016, May). \emph{Whose line is it anyway?: Where the borders are made up and the disasters don’t matter}. [Poster session]. 2016 American Psychological Society Conference, Chicago, IL.

\hangindent=0.7 cm **Gwozdz, D.**, **Snyder, A.**, Root, M. J., **Klapatch, L.**, & Spievak, E. R. (2016, May). \emph{What’s luck got to do with it?: The relationship between belief in luck and illusion of control}. [Poster session]. 2016 Association for Psychological Science Conference, Chicago, IL.

\hangindent=0.7 cm **Carlson, T.**, **Pollack, K.**, & Root, M. J. (2016, April). \emph{Disasters and border bias}. [Poster session]. 2016 Red River Psychology Conference, North Dakota State University, Fargo, ND.

\hangindent=0.7 cm **Carlson, T.**, **Pollack, K.**, & Root, M. J. (2016, April). \emph{Stigmas of border bias}. [Poster session]. 2016 Student Academic Conference, Minnesota State University: Moorhead, Moorhead, MN.

\hangindent=0.7 cm Stanley, C., & Root, M. J. (2016, January). \emph{What to cut and what to keep when teaching an introduction to psychology course}. [Conference workshop]. National Institute on the Teaching of Psychology Conference, Saint Pete Beach. FL.

\hangindent=0.7 cm Root, M. J., **Steele, J.**, & **Maldett, C.** (2009, February). \emph{Eugenics: Uncovering a hidden story from psychology’s past}. [Conference presentation]. 2009 Celebration of Inquiry, Coastal Carolina University, Conway, SC.

\hangindent=0.7 cm Root, M. J. (2008, July). \emph{Designing minds: Connecting psychology and cognitive science}. [Conference presentation]. 2008 Three Societies Conference, Oxford University, Oxford, England.

\hangindent=0.7 cm Root, M. J., Palm, L. J., Brallier, S., & Podeschi, C. (2008, March). \emph{Using online practice tests to improve test performance}. [Poster session]. 2008 Conference on the Scholarship of Teaching and Learning, Myrtle Beach, SC.

\hangindent=0.7 cm Root, M. J., Podeschi, C., Palm, L. J., & Brallier, S. (2008, February). \emph{Using computer based practice tests to enhance exam performance}. [Poster session]. 2008 Scholarship of Teaching and Learning Symposium, Coastal Carolina University, Conway, SC.

\hangindent=0.7 cm Root, M. J., & **Steele, J.** (2008, February). \emph{The role of podcasting in education}. [Conference presentation]. 2008 Celebration of Inquiry, Coastal Carolina University, Conway, SC.

\hangindent=0.7 cm Root, M. J., & **Steele, J.** (2008, February). \emph{Myth-making in the history of psychology: What students really need to know}. [Conference presentation]. 2008 Celebration of Inquiry, Coastal Carolina University, Conway, SC.

\hangindent=0.7 cm Root, M. J. (2003, August). \emph{Psychology at its boundaries: A study of three interdisciplinary movements}. [Conference presentation]. 2003 American Psychological Association Conference, Toronto, Canada.

\hangindent=0.7 cm Root, M. J. (2003, August). \emph{Unification through chaos: Can chaos theory unify psychology?} [Poster session]. 2003 American Psychological Association Conference, Toronto, Canada.

\hangindent=0.7 cm Root, M. J. (2003, June). \emph{Boundary-work in psychology: Three interdisciplinary movements}. [Conference presentation]. 2003 Cheiron: The International Society for the History of Behavioral and Social Sciences Conference, University of New Hampshire, Durham, NH.

\hangindent=0.7 cm Root, M. J. (2002, August). \emph{The strange attraction of psychology to chaos}. [Conference presentation]. 2002 American Psychological Association Conference, Chicago, IL.

\hangindent=0.7 cm Root, M. J. (2002, March). \emph{Cheater detection content effects on the Wason selection task}. [Poster session]. 2002 Eastern Psychological Association Annual Meeting, Boston, MA.

\hangindent=0.7 cm Root, M. J. (1998, August). \emph{The complex adapted mind: Rediscovering the mind with complexity and evolutionary psychology}. [Conference presentation]. 1998 Society for Chaos Theory in Psychology and the Life Sciences Conference. Boston University, Boston, MA.

\hangindent=0.7 cm Root, M. J. (1997, November). \emph{Introductory fundamentals of chaos and complexity theory}. [Invited address] 1997 Green Mountain College, Poultney, VT.

\hangindent=0.7 cm Root, M. J. (1997, July). \emph{George Kelly’s theory of personal constructs and chaos theory: A confluence of ideas}. [Conference presentation]. 1997 Society for Chaos Theory in Psychology and the Life Sciences, Marquette University, Milwaukee, WI.

\hangindent=0.7 cm Root, M. J. (1997, June). \emph{Chaos theory in counseling, psychotherapy and psychology}. Professional Development Workshop, Department of Counseling, Idaho State University, Pocatello, ID.

\hangindent=0.7 cm Root, M. J. (1997, February). \emph{Reconstructing Kelly’s construct system in phase space}. [Conference presentation]. 1997 Vermont Chaos Conference, Waterbury, VT.

# Awards and Fellowships

```{r awards}
tribble(
  ~ award, ~ from, ~ year, ~ where,
  "Teaching Recognition", "Panhellenic Association", "2014", "Bridgewater State University",
  "Student Academic Achievement Award", "Department of Psychology, Springfield College", "1998 --- 1999", "Springfield College",
  "Teaching Fellowship", "Department of Psychology, Springfield College", "1997 --- 1999", "Springfield College"
)%>% 
  detailed_entries(
    with = award,
    what = from,
    when = year,
    where = where
)
```

# Service and Professional Activities

```{r service}
tribble(
  ~ title, ~ service, ~ year, ~ where, ~detail,
  "External Service", "Activities", "Various", NA, "Archivist/Historian-elect for the Society for the Teaching of Psychology (2021)",
  "External Service", "Activities", "Various", NA, "Manuscript Reviewer for the Big South Undergraduate Research Symposium held at UNC-Asheville (2007)",
  "External Service", "Activities", "Various", NA, "Reviewer for PsycCRITIQUES (Contemporary Psychology: APA Review of Books) (2005 --- 2008)",
  "External Service", "Activities", "Various", NA, "Ad hoc Reviewer for the journal History of Psychology (2002)",
  "Bridgewater State University Service", "Activities", "2016 --- Present", "Bridgewater State University", "Center for the Advancement of Research and Scholarship (CARS) Advisory Committee (2020)",
  "Bridgewater State University Service", "Activities", "2016 --- Present", "Bridgewater State University", "Psychology Search Rules Committee",
  "Bridgewater State University Service", "Activities", "2016 --- Present", "Bridgewater State University", "Honors Committee",
  "Bridgewater State University Service", "Activities", "2016 --- Present", "Bridgewater State University", "Laboratory Advisory Committee",
  "Bridgewater State University Service", "Activities", "2016 --- Present", "Bridgewater State University", "Special 1-Year Retention Review Committee (2017)",
  "Minnesota State University Service", "Activities", "2015 --- 2016", "Minnesota State University", "Departmental IRB Committee",
  "Minnesota State University Service", "Activities", "2015 --- 2016", "Minnesota State University", "Liberal Arts and Science Curriculum Committee",
  "Coastal Carolina University Service", "Activities", "2005 --- 2009", "Coastal Carolina University", "University Teacher Evaluation Committee",
  "Coastal Carolina University Service", "Activities", "2005 --- 2009", "Coastal Carolina University", "Sociology Faculty Search Committee",
  "Coastal Carolina University Service", "Activities", "2005 --- 2009", "Coastal Carolina University", "Celebration of Inquiry College Liasons Committee",
  "Coastal Carolina University Service", "Activities", "2005 --- 2009", "Coastal Carolina University", "Psychology Faculty Search Committee",
  "Coastal Carolina University Service", "Activities", "2005 --- 2009", "Coastal Carolina University", "Psychological Communications Committee",
  "University of New Hampshire Service", "Activities", "2003", "University of New Hampshire", "Manuscript Reviewer for Cheiron, The International Society for the History of Behavioral and Social Sciences 35th Annual Conference", 
  "University of New Hampshire Service", "Activities", "2003", "University of New Hampshire", "Conference Coordinator, The International Society for the History of Behavioral and Social Sciences 35th Annual Conference",
  "Springfield College Service", "Activities", "1998", "Springfield College", "Chairperson, Scholarship Committee",
  "Springfield College Service", "Activities", "1998", "Springfield College", "Conference Coordinator, Sixth Annual Winter Chaos Conference",
  )%>% 
  detailed_entries(
    with = title,
    what = service,
    why = detail,
    when = year,
    where = where
)
```

# Professional Organization Memberships

* Association for Psychological Science
* Society for the Teaching of Psychology
* Northeastern Evolutionary Psychology Society

# Professional References

Sandra Neargarder, Ph.D., Dept. Chair, 
Psychology Dept., 90 Burrill Ave., 
Bridgewater State University, Bridgewater, MA 02325, 
sneargarder@bridgew.edu,
508-531-2378

Christine Malone, Ph.D., Dept. Chair,
Psychology Dept., 360 G Bridges Hall,
Minnesota State University Moorhead, MN 56563,
malonech@mnstate.edu,
218-477-2804

William R. Woodward, Ph.D.,
Dept. of Psychology, Conant Hall, 10 Library Way,
University of New Hampshire, Durham, NH 03824,
William.Woodward@unh.edu,
603-862-3199
